A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 methodology.tex
reorg and explain more about why 3

Note that the tree depicted in Figure~\ref{fig:extraction} is not an AST; rather, it represents an ASTDiff. The number of paths in the ASTDiff does not directly correspond to the number of changed elements in the source code. Instead, it is determined by the structural differences between the two ASTs of the code versions. The paths in the ASTDiff capture the changes in the code structure between the two versions, allowing us to analyze and extract relevant information for further processing.

>>>>

Note that the tree depicted in Figure~\ref{fig:extraction} is not an AST; rather, it represents an ASTDiff. The paths in the ASTDiff capture the changes in the code structure between the two versions, allowing us to analyze and extract relevant information for further processing. The number of paths in the ASTDiff does not directly correspond to the number of changed elements in the source code. Instead, it is determined by the structural differences between the two ASTs of the code versions.

In our example, we add a \verb+&+ borrow operator to the variable \verb+tail+, which gives rise to an ASTDiff path introducing a new parent node (\verb+ExprReference+) for \verb+tail+. We also add a \verb+clone()+ method call. This addition gives rise to two ASTDiff paths: one indicating that the \verb+head+ node is touched and one indicating the new sibling node for \verb+head+ representing the \verb+clone()+. (Among the terminals, we only keep \verb+clone+ in our paths, as it is a BC-related keyword.) One path for the \verb+&+ borrow operator and two for the call to \verb+clone()+ result in three paths in the ASTDiff, even though only two arguments have been modified.
